Sell Prevention and Buy Cure: An Exploration of Indirect Conflicts

### 2013-12-09 iced-2013/paper.tex
Added ic figure and highlighted implications section.

Two types of conflicts have attracted the attention of researchers, \textit{direct} and 
\textit{indirect conflicts}. Direct conflicts involve immediate workspace concerns such as developers editing the same
artifact. Tools have been created and studied for direct conflicts
~\cite{Xiang:2008:ERT, Biehl:2007:FVD, Sarma:2009:TIV, Khurana:2009:PFC} with relatively good success and 
positive developer feedback. Indirect conflicts involve source code change influences such as making a sour code change 
which influences behavior negatively in another location in the system. Indirect conflict tools however, have
not shared the same success as direct conflict 
tools~\cite{Sarma:2007:TSA, Holmes:2010:CAR, Trainer:2005:BGT, Servant:2010:CPI, Borici:2012:CHA}.

While indirect conflict tools have shown potential from developer studies, some of the same problems continue
to arise throughout most, if not all tools. The most prevalent issue is that of false positives and information
overload. Through case studies, developers have noted that current indirect conflict tools provide too many 
false positive results leading to information overload and the tool eventually being
ignored~\cite{Sarma:2007:TSA, Servant:2010:CPI}. A second primary issue is that of dependency identification and
tracking. Many different dependencies have been proposed and used in indirect conflict tools such as method 
invocation~\cite{Trainer:2005:BGT}, and class signatures~\cite{Sarma:2007:TSA} with varying success, but the 
identification of failure inducing changes, other than those which are already identifiable by other means such
as compilers, and unit tests, to these dependencies still remains an issue. Dependency tracking issues are
also compounded by the scale of many software development projects leading to further information overload.
Lastly, social factors such as Cataldo et al.~\cite{Cataldo:2006:ICR} notion of socio-technical
congruence have been leveraged in indirect conflict tools~\cite{Kwan:2011:ESC, Begel:2010:CDE, Borici:2012:CHA}.
However, issues again of information overload, dependencies (in developer organizational structure), and scalability 
come up.

@@

@@

The largest implication for future research found in this paper is the need for continued study of the open question
``Which of prevention or cure is more effective for software development and indirect conflicts?''. This simple question will undoubtedly 
produce extremely complex answers. With software developers focusing their current efforts on curative measures, for
indirect conflicts, suggests
that while it may not be the most effective, it may be the easiest road for developers to take. This may be the path of
least resistance, but it may not be optimal. Software engineering as a whole should strive to answer this question or
provide more insight into possibilities, as its answer may determine many future actions taken by the research community.

@@

A second implication for research more directly related to awareness, is the need to further characterize the
mismatch between awareness approaches and tools as developed in the research community and awareness needs as perceived
by industry.
As was identified in the previous discussion, while current understanding suggests that awareness of all events related to ones work
produces a more coherent understanding of a person's environment, developers find this to be overly time consuming
to the point where they only want to be aware of events which require action on their part. This difference, of what 
should be and what is, should be further understood to combat future potential failures in
tool development or theories attempted to be used in practice.

@@

The direct implication this research has on tool creation is that of current adoption among developers. As was stated,
developers are more keen to invest their time at the detection and cure / resolution stages of indirect conflicts. That being 
said, focus at these two stages for tool developer will lead to larger adoption among developers.
It should be noted here that detection must come with an almost zero rate of false positives as
current tools (unit and integration and user testing), while they may not have 100\% recall, have almost 100\% precision.

The more indirect implication of this research on tool creation is that of improving existing tools. While not all existing
tools are used for indirect conflicts alone (automatic debugging~\cite{Zeller:2005:WPF}, unit tests, etc), most of these tools
have need for rapid expansion, according to developers, for dealing with indirect conflicts. The ability to have unit tests
automatically written for a given software object's contract, the ability to find a change  in an external project
which has broken a developer's own project, or any automation of the existing detection and resolution stages of indirect
conflicts are what developers currently seek. But of course, most of these implications rely on the improvement of 
static analysis tools.

@@

We have shown through the findings of RQ1 why indirect conflicts occur, when indirect conflicts are more likely to
occur, as well as what types of software objects are susceptible to these conflicts. Results of RQ 2 have shown
how developers in industry currently handle the prevention detection and solving of indirect conflicts. And Lastly, findings of RQ3
have provided a foundation as to why past techniques and tools have had low adoption rates and where
researchers should focus their current and future efforts in handling indirect conflicts.

>>>>

Two types of conflicts have attracted the attention of researchers, \textit{direct} and 
\textit{indirect conflicts}. Direct conflicts involve immediate workspace concerns such as developers editing the same
artifact. Tools have been created and studied for direct conflicts
~\cite{Xiang:2008:ERT, Biehl:2007:FVD, Sarma:2009:TIV, Khurana:2009:PFC} with relatively good success and 
positive developer feedback. Indirect conflicts involve source code change influences such as making a sour code change 
which influences behavior negatively in another location in the system (Figure~\ref{fig:ic}). Indirect conflict tools however, have
not shared the same success as direct conflict 
tools~\cite{Sarma:2007:TSA, Holmes:2010:CAR, Trainer:2005:BGT, Servant:2010:CPI, Borici:2012:CHA}.

While indirect conflict tools have shown potential from developer studies, some of the same problems continue
to arise throughout most, if not all tools. The most prevalent issue is that of false positives and information
overload. Through case studies, developers have noted that current indirect conflict tools provide too many 
false positive results, leading to information overload and the tool eventually being
ignored~\cite{Sarma:2007:TSA, Servant:2010:CPI}. A second primary issue is that of dependency identification and
tracking. Many different dependencies have been proposed and used in indirect conflict tools such as method 
invocation~\cite{Trainer:2005:BGT}, and class signatures~\cite{Sarma:2007:TSA} with varying success, but the 
identification of failure inducing changes, other than those which are already identifiable by other means such
as compilers, and unit tests, to these dependencies still remains an issue. Dependency tracking issues are
also compounded by the scale of many software development projects leading to further information overload.
Lastly, social factors such as Cataldo et al.~\cite{Cataldo:2006:ICR} notion of socio-technical
congruence have been leveraged in indirect conflict tools~\cite{Kwan:2011:ESC, Begel:2010:CDE, Borici:2012:CHA}.
However, issues again of information overload, dependencies (in developer organizational structure), and scalability 
come up.

@@

\begin{figure*}[tb!]
\centering
\includegraphics[width=0.9\textwidth]{images/indirect_conflict.png}
\caption{An example of an indirect conflict. Bobby has changed method bar() which has negatively affected method
func() through the chain of invocations.\label{fig:ic}}
\end{figure*}

@@

\textbf{Prevention versus Cure}
The largest implication for future research found in this paper is the need for continued study of the open question
``Which of prevention or cure is more effective for software development and indirect conflicts?''. This simple question will undoubtedly 
produce extremely complex answers. With software developers focusing their current efforts on curative measures, for
indirect conflicts, suggests
that while it may not be the most effective, it may be the easiest road for developers to take. This may be the path of
least resistance, but it may not be optimal. Software engineering as a whole should strive to answer this question or
provide more insight into possibilities, as its answer may determine many future actions taken by the research community.

@@

\textbf{Awareness Theory to Model Real World}
A second implication for research more directly related to awareness, is the need to further characterize the
mismatch between awareness approaches and tools as developed in the research community and awareness needs as perceived
by industry.
As was identified in the previous discussion, while current understanding suggests that awareness of all events related to ones work
produces a more coherent understanding of a person's environment, developers find this to be overly time consuming
to the point where they only want to be aware of events which require action on their part. This difference, of what 
should be and what is, should be further understood to combat future potential failures in
tool development or theories attempted to be used in practice.

@@

\textbf{Give Developers What They Want}
The direct implication this research has on tool creation is that of current adoption among developers. As was stated,
developers are more keen to invest their time at the detection and cure / resolution stages of indirect conflicts. That being 
said, focus at these two stages for tool developer will lead to larger adoption among developers.
It should be noted here that detection must come with an almost zero rate of false positives as
current tools (unit and integration and user testing), while they may not have 100\% recall, have almost 100\% precision.

\textbf{Stronger Source Code Analysis}
The more indirect implication of this research on tool creation is that of improving existing tools. While not all existing
tools are used for indirect conflicts alone (automatic debugging~\cite{Zeller:2005:WPF}, unit tests, etc), most of these tools
have need for rapid expansion, according to developers, for dealing with indirect conflicts. The ability to have unit tests
automatically written for a given software object's contract, the ability to find a change  in an external project
which has broken a developer's own project, or any automation of the existing detection and resolution stages of indirect
conflicts are what developers currently seek. But of course, most of these implications rely on the improvement of 
static analysis tools.

@@

We have shown through the findings of RQ1 why indirect conflicts occur, when indirect conflicts are more likely to
occur, as well as what types of software objects are susceptible to these conflicts. Results of RQ2 have shown
how developers in industry currently handle the prevention detection and solving of indirect conflicts. And Lastly, findings of RQ3
have provided a foundation as to why past techniques and tools have had low adoption rates and where
researchers should focus their current and future efforts in handling indirect conflicts.
